Scientific Reports Title to see here (20 words or less)

### 2016-09-20 draft1.tex
a few changes to sensitivity section

\subsection{Global Sensitivity}
We used the Morris method of sampling to generate a family of parameter sets, ranging from $\pm$25\% of the nominal parameter values, with the exception of $h_0$, which was bounded between [.8, 2.0], corresponding to a resting heart rate between 48 and 120 bpm.\cite{morris1991factorial} We found that this range of parameters resulted in physiologically acceptable heart rates. As heart rates are a function of time, it was neccessary for us to collapse the time dimension to perform sensitivity analysis. We used fPCA (functional principal component analysis) to convert the heart rate curves into weights ($\omega_i$) and eigenfunctions $(\xi_i(t))$ so that $h_j(t)=\sum_i \omega_i \xi_i(t)$, and then performed sensitivity analysis on the weights generated for each patient. \cite{sumner2012methodology} We then grouped the patients by cluster, and calculated the average of $\mu^*$, the estimate of the mean of distrubution of the absolute values of the elementry effects. For each cluster, we calculated the overall standard deviation, $\sigma$, by summing all of the variances and then taking the square root. \cite{1_normal sum distribution} The results are shown in \ref{fig:Cluster1Morris} and \ref{fig:Cluster2Morris}.

>>>>

\subsection{Global Sensitivity}
We used the Morris method of sampling to generate a family of parameter sets, ranging from $\pm$25\% of the nominal parameter values, with the exception of $h_0$, which was bounded between [.8, 2.0], corresponding to a resting heart rate between 48 and 120 bpm.\cite{morris1991factorial} We found that this range of parameters resulted in physiologically acceptable heart rates. As heart rates are a function of time, it was neccessary for us to collapse the time dimension to perform sensitivity analysis. We used fPCA (functional principal component analysis) to convert the heart rate curves into weights ($\omega_i$) and eigenfunctions $(\xi_i(t))$ so that $h_j(t)=\sum_i \omega_i \xi_i(t)$, and then performed sensitivity analysis on the weights generated for each patient. \cite{sumner2012methodology} We then grouped the patients by cluster, and calculated the average of $\mu^*$, the estimate of the mean of distrubution of the absolute values of the elementry effects. For each cluster, we calculated the overall standard deviation, $\sigma$, by summing all of the variances and then taking the square root. \cite{1_normal sum distribution} The results are shown in \ref{fig:Cluster1Morris} and \ref{fig:Cluster2Morris}. The results are nearly identical between the two clusters, with the ranking of the six most sensitive paramaters (as given by the largest values of $\mu^*$) being the same in both clusters, with $m_{nor}$ being the parameter with the largest effect on the model's output. The parameter with the largest standard deviation, indicative of it depending on other paramters in the model, was the resting heart rate.
